---
title: "Facilities & Resources"
output:
  distill::distill_article:
    self_contained: false
    anchor_sections: FALSE
    css: [theme_inferno_black.css]
site: distill::distill_website
favicon: microscope_white.png
---

```{r, eval=TRUE, warning=FALSE, message=FALSE, echo=FALSE}

knitr::opts_chunk$set(echo = FALSE)

```
  
### Facilities        
  
#### MOTION - MIcrobiome TransmissION Research Laboratory (Kelly Lab)  
  
The MOTION (MIcrobiome TransmissION) research laboratory at the University of Pennsylvania comprises six wet bench workspaces, two BSL-2 biosafety cabinets, and four -80C freezers for biospecimen storage. Laboratory inventory management is performed with Labvantage software, which is hosted on secure university servers, and which provides barcoded label generation for all collected biospecimens and products of post-collection processing. On-site laboratory equipment includes two PCR hoods for DNA extraction and library preparation work, a thermocycler for nucleic acid amplification, a quantitative PCR instrument, a microplate reader (BMG Labtech) for bacterial growth curve assays, two Oxford Nanopore Minion instruments and a high-memory Windows workstation for long-read sequencing. The laboratory space includes two refrigerators for reagent storage and three incubators, which will be used for the described bacterial culture approaches. A full-time laboratory manager and three full-time laboratory technicians occupy the space. Dr. Brendan J. Kelly, MD, MS, Principal Investigator, directs the MOTION Research Laboratory.  
  
#### Clinical Microbiology Laboratory at the Hospital of the University of Pennsylvania (HUP)  
  
Subject recruitment will depend on identifying hospitalized subjects who are diagnosed with hospital-acquired pneumonia (HAP) or ventilator-associated pneumonia (VAP) via clinical respiratory tract bacterial culture. Causative bacterial pathogens will be identified by clinical cultures processed at the HUP Clinical Microbiology Laboratory. The HUP Clinical Microbiology Laboratory, located on the 4th floor of the Gates Building, is a fully accredited clinical laboratory by the College of American Pathology, containing approximately 5,500 square feet of space. The laboratory meets requirements for the handling of Class II pathogens, and contains many biosafety cabinets, centrifuges, semiautomated susceptibility testing equipment (Vitek 2), Matrix-Assisted Laser Desorption/Ionization-Time Of Flight (MALDI-TOF) mass spectrometry, facilities for media preparation, microscopes, and incubators. It is a full service 24/7 laboratory, with 28 full time medical technologists, two supervisors, and three doctoral level directors. It performs about 0.5 million tests per year.  
  
#### PennCHOP Microbiome Program Sequencing and Analytics Core  
  
The Penn-CHOP Microbiome Program comprises High-Throughput Sequencing and Analytical Cores. The former supports next-generation sequencing of microbiome specimens by providing sample aliquoting, DNA extraction, quantitative PCR, library preparation, and sequencing services. Sequencing instruments include an Illumina NovaSeq 6000 instrument, HiSeq 2500 instrument, MiSeq instruments, and Oxford Nanopore instruments. The High-Throughput Sequencing Core also includes two automated liquid handling robots for high-throughput processing. The Analytical Core provides bioinformatics and analysis support services to match sequence data generation, including quality checks, removal of host genomic sequences, automated pipelines to assess bacterial, fungal, and viral taxa, as well as alignments to genes of known interest. High-capacity network lines connect the Analytical Core to the Sequencing Core, and to the CHOP supercomputing facility in Allentown, PA. The Core is staffed by three full time programmer/analysts and is supported by a network of consulting statisticians. Dr. Kelly has collaborated extensively with the core, completing several large translational microbiome studies supported by the Centers for Disease Control and Prevention (CDC).  
  
#### Penn Medicine Digital Academic Research Transformation (DART)  
  
The DART high-performance computing system includes 144 IBM iDataPlex Nodes (Red Hat Linux 6.4) with 16 physical cores per node, 192 or 256 GB of RAM per node, 2 Petabytes of IBM SONAS Disk Storage, and 1.8 Petabytes of mirrored archive tape storage. A high-memory virtual machine server has already been established to support the high-throughput sequencing analysis, including whole genome sequence (WGS), as well as the Bayesian modeling activities of Principal Investigator. The virtual machine includes SPAdes for whole genome assembly, the Sunbeam pipeline (including MetaPhlAn3 and StrainPhlAn) for shotgun metagenomic analysis, R statistical software, and Stan Hamiltonian Monte Carlo.  

#### PennMedicine Clinical Sites  
  
MOTION Laboratory translational studies have been closely integrated with acute care facilities affiliated with the University of Pennsylvania Health System (UPHS or PennMedicine). Dr. Kelly has a track record of successful translational microbiome study recruitment from the planned sites. The Hospital of the University of Pennsylvania (HUP) is the primary recruitment site and is a quaternary care medical center. There are over 33,000 admissions, 633,000 outpatient visits, and 54,000 ED visits annually at HUP, the system’s largest hospital. HUP’s primary service area of encompasses 25% of the population of Philadelphia including all of West Philadelphia, Southwest Philadelphia, and portions of South Philadelphia. It is an ethnically and racially diverse community of 368,000 residents; 68% of the population is African-American, 27% White, 3.4% Asian, and 1.5% Latino.  

#### University Library and Other Resources    
  
Dr. Kelly maintains primary research office space within Blockley Hall, which houses over 140 offices located on five contiguous floors. Each floor includes 7,500 square feet of recently renovated space. The total available space yields approximately 34,000 square feet that can be assigned. Within this space, there also exist one seminar/lecture room per floor with the capacity for 50 people, three large 160-person conference rooms, and several smaller conference rooms. Blockley Hall is adjacent to HUP and other Perelman School of Medicine buildings. All MOTION Lab activities benefit from the outstanding educational and research resources of a nationally-ranked university. The University of Pennsylvania Medical Center is one of the top academic health science centers in the nation, in terms of research support received from the National Institutes of Health. As a result of their access to university-wide resources, the principal and co-investigators conduct their research in a highly collaborative atmosphere that integrates clinical and basic research with the goal of immediate translation to improve patient care. The medical school library includes extensive digital resources so support all research activities.  
  
  
### Equipment        
  
The MOTION (Kelly) research laboratory space contains Labvantage label printers for biospecimen indexing, -80C freezers for initial biospecimen storage, three incubators for bacterial culture, two polymerase chain reaction (PCR) hoods for DNA extraction, and thermocyclers for library preparation. It also includes a QuantStudio 5 RT-qPCR instrument and has shared access to a QX200 ddPCR instrument on the same floor of the Johnson Pavilion building. The nearby PennCHOP Microbiome Program Sequencing and Analytics Core contains an Illumina NovaSeq 6000 sequencer, which is used for metagenomic sequencing of human-subject samples, as well as select bacterial whole-genome sequencing from cultured isolates. Analysis is supported by an already-established high-memory virtual machine on Penn Medicine Digital Academic Research Transformation (DART) server, which includes Sunbeam, MetaPhlAn4, and StrainPhlAn for metagenomic sequence binning and assignment; iRep and bPTR tools for origin of replication analysis; SPAdes for de novo whole genome assembly, MAFFT for multisequence alignment, and IQ-TREE for phylogenetic analyses. Our server also includes R statistical software and Stan Hamiltonian Monte Carlo for implementing Bayesian dynamic system modeling.  
  

```{r equipment_inventory, eval=TRUE, warning=FALSE, message=FALSE, echo=FALSE, layout="l-body-outset", fig.width=6}

#' #################################
#' load libraries and set seed
#' #################################
library(tidyverse)
library(gt)
library(gtExtras)


#' #################################
#'  read and format meeting data
#' #################################

read_csv("equipment/motion_equipment_dat.csv") |> 
  identity() -> equipment_dat

equipment_dat |> 
  gt() |> 
  gt::sub_missing() |> 
  gtExtras::gt_theme_nytimes() |> 
  gt::tab_options(table.background.color = "#FFFFFF00")


```


 <br>

 <br>

 <br>

 <br>

 <br>

 <br>
  
 <br>

 <br>

 <br>


